\subsection{Choosing Significators}
\begin{frame}[t]{Choosing Significators}
Masha'allah's method for choosing which planets will act as significators for the \textsl{querent} (the person asking the question) and the \textsl{quesited} (question's subject matter) can be reduced to:
\begin{itemize}
\item Does the ruler of the Ascendant (L1) aspect the 1st House?
	\begin{itemize}
		\item Yes? use L1 as the main significator of the querent and the \Moon\ as their partner
		\item No? does L1 aspect another planet that aspects the 1st House or one who does so indirectly by that 2nd planet aspecting a 3rd planet that aspects the 1st House?
			\begin{itemize}
				\item Yes? work through these planets and use the \Moon\ as a their partner
				\item No? repeat the same steps using the \Moon\ instead of L1 and if she is suitable, make her the main significator and L1 her partner
			\end{itemize}
	\end{itemize}
\item If neither L1 nor the \Moon\ are usable, see which of the two is the first to leave its sign and judge the effect from that planet's first joining to another planet after entering its new sign, using the other planet (L1 or \Moon) as their partner;\footnote{Normally the \Moon\ is the first to change signs as she moves faster than the other planets.} noting that matters will be slow and inactive until the sign change occurs.
\end{itemize}

\end{frame}
% ------------------------------------------------------------------------------------------
\begin{frame}[t]{Choosing Significators Continued}
\begin{itemize}
\item The main significator of the quesited will be the ruler of the house signifying the matter i.e.  Wealth, ruler of 2nd House (L2); Siblings, ruler of the 3rd House (L3); Friends, ruler of the 11th House (L11); Children, ruler of the 5th House (L5), etc.
\item Planets in the 1st House and the house signifying the matter at hand have a bearing on the conditions surrounding the matter BUT they do not determine the outcome of the matter; that depends on the chosen significators, their aspects and condition.\footnote{Robert Hand says \textsl{"Rulers of houses in general are more important to outcomes than occupants of houses."}(fn1p9)}
	\begin{itemize}
		\item planets in the affected houses, if they are received by their dispositor, \textsl{"indicate the goodness and worthiness of the thing sought"}, if they are not received by their dispositor (which implies no aspect between the two), then they indicate impediments and the worthlessness of what is sought
	\end{itemize}
\item If the ruler of the Asc or the \Moon\ does not aspect the 1st House they are to be considered \textsl{evil and impeded}
\end{itemize}

\end{frame}