\begin{frame}[t]{Hyleg and Alcochoden}
All of Masha'allah's examples relate to Horary questions; however, he did include some rather garbled instructions relating to identifying the Hyleg (the releaser) and the Alcochoden (the giver of years).

\textbf{The Hyleg} \\
The Hyleg can be one of the \Sun, \Moon, \Fortune, SAN or Ascendant.\\
The rules used to qualify each are:\footnotemark[1] \\
\begin{itemize}
\item[\Sun] in the 1st, 10th, 7th, or 11th and received by its domicile or exaltation ruler
\item[\Moon] in an angular or succedent house if received by its domicile or exaltation ruler
\end{itemize}

\textbf{\Fortune\ or SAN or Asc} in an angular or succedent house, joined to [implies reception] its \textbf{term} or domicile ruler, in which case that ruler becomes the Hyleg otherwise the element itself is Hyleg

Start from the \Sun\ for diurnal births, the \Moon\ for nocturnal births. If they fail to meet the criteria move on to the other light and if it doesn't meet the criteria check \Fortune, followed by the correct pre-natal syzygy, its counterpart, and last of all the Asc.

\footnotetext[1]{Ptolemy's 5° rule applies when determining which house a planet is in.}
\end{frame}
% --------------------------------------
\begin{frame}[t]{The Hyleg Continued}
My reading of the text re: \Fortune, SAN, and Asc is somewhat unorthodox; however, I believe this is what the text is saying:\\

\vspace{0.5cm}
\begin{quote}
"But if it is not the ruler of the terms of the Part of Fortune, or the ruler of the house that is joined to it---that is, to the Part of Fortune---\textbf{then the Part of Fortune [itself] will rule, and it will by Hyleg;} and from its ruler is known the giving of years... [JH p50 emphasis added]
\end{quote}
Similar wording is used for the SAN and Asc.  \\

\vspace{0.5cm}
\begin{quote}
"However, if...the conjunction and the lord of its bound, or the lord of the domicile in which $<$it$>$ is [located] is \textbf{not joined} to the degree of the conjunction,...\textsl{the degree of this conjunction will by Hyleg.}" [RH p51 emphasis added]
\end{quote}


Both statements imply that the term or domicile ruler becomes the Hyleg \textsl{if it aspects the element}; otherwise, the element itself is Hyleg. The more common teaching is that if the element is aspected by its ruler, the element \textsl{itself} becomes hyleg. As I've never had much luck using the Hyleg and Alcochoden I've decided to experiment with them again using this approach.
\end{frame}
% -----------------------------------------------
\begin{frame}[t]{The Alcochoden}
If the \Sun\ or \Moon\ is the Hyleg, the domicile or exaltation ruler in aspect becomes the the \textsl{alcochoden} or "giver of years". \\

\vspace{0.2cm}
If the term or domicile ruler of \Fortune, SAN, or Asc is the hyleg, their domicile ruler becomes the alcochoden; if \Fortune, SAN, or Asc is, itself, the hyleg, their domicile ruler becomes the alchochoden.\\

\vspace{0.2cm}
The alcochoden gives its major, middle, or minor years according to its condition:
\begin{description}
\item[Major:] if direct, in the 1st, 7th, or 10th, not USB or in its fall \\
	if in its own dignities, oriental and in the 4th, 5th, or 11th
\item[Middle:] in the 11th or 5th, oriental peregrine \\
	in 2nd or 8th and in their own dignities or peregrine, not in Fall or a pit or detriment (?) \\
	in the 9th, dignified and oriental
\item[Minor:] in the 6th or 12th and of the chart sect, not in its Fall \\
	in its Fall in the 12th or Retrograde in the 6th will give its minor years as months \\
	USB, retrograde in Fall in 12th or 6th will minor years as days
	
\end{description}

\end{frame}
% -----------------------------------------
\begin{frame}[t]{The Alcochoden Continued}
If both benefics aspect the alcochoden, their years are increased 1 year for each rising degree they occupy in their sign. And similarly, their years are decreased 1 year for each rising  degree they occupy in their sign if the are in the aspect of a malefic. \\

\vspace{0.25cm}
If they are within 8° of \NorthNode\ or \SouthNode\ their years are decreased by 1/4.

\textbf{Usage:}
Direct the Hyleg by Primary Direction and thru the Terms to the body or aspect of malefics. If the timing agrees with the years given by the alcochoden, check to see if benefics also aspect the same degrees, in which case they will be freed from death or suffering pain. The timing is based on the ascension degrees covered with 1° equalling 1 year.

\end{frame}

